### 2017-03-16 main.tex
Table 2 is still being generated. This is just an interim so I can work from home...

\fig{fig:song} shows a typical song. The image is produced by
averaging the aligned spectrograms, in this case for the bird lny64.
Six target trigger points are shown for this song, at 150, 200, 250,
300, 350, and 400 milliseconds after the beginning of the aligned
samples, as indicated by the red lines, and referred to henceforth as
$t^*_1\ldots t^*_6$ respectively.  For clarity, the rectangles show a
shorter recognition window than our standard: here 30 ms, but still
spanning 1--8 kHz, for each target time in the song.\marginpar{Is this
  OK?  Should I update to a 50-ms window? They'll overlap!}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Fig2}
  % 9x10 inches
  % Fonts: Helvetica, scaled 130%
  \caption{Each plot shows one network output unit's responses to all
    2818 presentations of lny64's song shown in \fig{fig:song}.  For
    simplicity, we show only the syllables $t^*_1$, $t^*_4$, and
    $t^*_6$, and we do not show the non-response to presentation of non-song. The horizontal axis is time relative to the beginning of
    the aligned song, and the vertical axis is an index for the 2818
    individual song presentations. The grey shading shows the audio
    amplitude of song Y at time T. Detection events on training songs
    are shown in cyan, with detections of unseen test songs in red.  To provide an intuition of intra-song variability, songs have been
    stably sorted by the time of detection events; thus, each of the
    three detection graphs shows the songs in a different order.}
  \label{fig:detection_raster}
\end{figure}

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.
%Accuracy \marginpar{Should be! Verify! And/or explain that there is a bug in the LabVIEW implementation, if there in fact is. ALSO need to present a picture of the test syllable or etc \dots} is identical across the three detectors.
\noprint{
  Typical confusion matrices for these syllables are:

@@

\begin{table}
  \begin{tabular}{rc|rr}
    Bird & Target time & \% True positives & \% False positives \\ \hline
    A&$ t^*_1$ & 99.72 &  0.0025 \\ % lny64
    &$ t^*_2$ & 99.81 &  0.00053 \\
    &$ t^*_3$ & 99.78 &  0.00062 \\
    &$ t^*_4$ & 99.69 &  0.00082 \\
    &$ t^*_5$ & 99.75 &  0.00028 \\
    &$ t^*_6$ & 99.54 &  0.0012 \\
    B&$ t^*$ & 99.370992640000068   0.003887539045000 \\ % lny46
    C&$ t^*$ & 99.218862389999998   0.001205787775200 \\ % lny42
    D&$ t^*$ & 99.342842499999975   0.00260723410200  \\ % lny4rb
    E& $t^*$ & 99.726635259999981   0.003169430259900 \\ % lr28
    E& $t^*$ & 99.464679732673261   0.004515502156436 \\ % lr12
    E& $t^*$ & 99.862406879999966   0.001215710723800 \\ % lr13
    E& $t^*$ & 99.646613329999980   0.003110002775000 % lr77
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

>>>>

\fig{fig:song} shows a typical song. The image is produced by
averaging the aligned spectrograms for the bird lny64.  Six target
trigger points are shown for this song, at 150, 200, 250, 300, 350,
and 400 milliseconds after the beginning of the aligned samples, as
indicated by the red lines, and for convenience will be referred to
henceforth as $t^*_1\ldots t^*_6$ respectively.  For clarity, the
rectangles show a shorter recognition window than our standard: here
30 ms, but still spanning 1--8 kHz, for each target time in the
song.\marginpar{Is this OK?  Should I update to a 50-ms window?
  They'll overlap.}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Fig2}
  % 9x10 inches
  % Fonts: Helvetica, scaled 130%
  \caption{Each plot shows one network output unit's responses to all
    2818 presentations of lny64's song shown in \fig{fig:song}.  We
    show only the syllables $t^*_1$, $t^*_4$, and $t^*_6$, and we do
    not show the non-response to presentation of non-song. The
    horizontal axis is time relative to the beginning of the aligned
    song, and the vertical axis is an index for the 2818 individual
    song presentations. The grey shading shows the audio amplitude of
    song Y at time T. Detection events on training songs are shown in
    cyan, with detections of unseen test songs in red.  To provide an
    intuition of intra-song variability, songs have been stably sorted
    by the time of detection events; thus, each of the three detection
    graphs shows the songs in a different order.}
  \label{fig:detection_raster}
\end{figure}

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see.
%Accuracy \marginpar{Should be! Verify! And/or explain that there is a bug in the LabVIEW implementation, if there in fact is. ALSO need to present a picture of the test syllable or etc \dots} is identical across the three detectors.
\noprint{
  Typical confusion matrices for these syllables are:

@@

\begin{table}
  \begin{tabular}{rc|rr}
    Bird & Target time & \% True positives & \% False positives \\ \hline
    A&$ t^*_1$ & 99.72 &  0.0025 \\ % lny64
    &$ t^*_2$ & 99.81 &  0.00053 \\
    &$ t^*_3$ & 99.78 &  0.00062 \\
    &$ t^*_4$ & 99.69 &  0.00082 \\
    &$ t^*_5$ & 99.75 &  0.00028 \\
    &$ t^*_6$ & 99.54 &  0.0012 \\
    B&$ t^*$ & 99.370992640000068   &0.003887539045000 \\ % lny46
    C&$ t^*$ & 99.218862389999998   &0.001205787775200 \\ % lny42
    D&$ t^*$ & 99.342842499999975   &0.00260723410200  \\ % lny4rb
    E& $t^*$ & 99.726635259999981   &0.003169430259900 \\ % lr28
    E& $t^*$ & 99.464679732673261   &0.004515502156436 \\ % lr12
    E& $t^*$ & 99.862406879999966   &0.001215710723800 \\ % lr13
    E& $t^*$ & 99.646613329999980   &0.003110002775000 % lr77
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}
